Digital Privacy and Cryptography

### 2014-12-06 LaTex/paper.tex
Included TSL discussion

\documentclass[12pt]{article}
\usepackage{latexsym}
\usepackage{setspace}
\doublespacing

@@

There a wide range of Private Enhancing techniques using Crypotgraphy. This paper will focus on Private Digital Credentials, Type X remailers, and Onion Routing focusing on how these can allow for digital privacy. A few defintions to establish are anonymity and pseudonymity. Anonymity systems are built to make one-way communication while getting information private while pseudonymity are built to allow for two-way communcation by using a pseudonym to help keep information private. \cite{GoldbergTwo}

@@

\section{Type X Remailers}\label{sec:type-x}
What is it?
These anonymous remailer which aim to allow users to allow for e-mail communcations without losing privacy. There are four differ Versions of Type X Remailers, Type O, Type I, Type II and Type III with Type III providing the most functionality. All the different versions work differently where some are anonymity systems and others are pseudonym systems. Type 0 is the easier remailer to understand. The basic idea is mail to sent to the system which strips all information which could be used to identify the user and distributes the mail to the intender receiver.

Type III also knows as Mixminion had its first  release in 2002. Mixminion aimed to support pseodonymity in which Type II had poor support\cite{GoldbertTwo}. The project had its own git on Github which has not been updated since 2011. According to their design document which can be found on their website, the designers had the following goals simplicity for clients, simple to deploy, and drop packets-level compatibility with Mixmaster (Type II).  Mixminon uses a free-route mix but does not implement reusable reply blocks.

Anonymous Remailers can be used to send communications anonymously. However Type III  has been said to not be trusted for anonymity \cite{GoldbertTwo}. The previous version have their technical issues. This details would need to be sorted out before this techonlogy can be replied upon.

@@

\section{Good Life Examples}\label{sec:real-life}
Wickr is a new messenger which is available on Google Play store, Apple App Store, and even for desktop. It is uses peer-to-peer encryption and enables users to send encrypted messages.  According to its website it uses hashed all device information with SHA256 and encrypts all data with AES256. The Wickr server only handles encrypted messages and delete the message upon delivery. The server also never directly interacts with devices identifiers but onlt the hashes of them. Wickr has received four and a half stars on the Apple store from 80 different ratings and has a similar rating on the Google Play store.

@@

\bibitem{Marks}
	Marks, G. (2014, March 4). Here's Why You May Be Buying BlackBerry Again. Retrieved December 5, 2014, from http://www.forbes.com/sites/quickerbettertech/2014/03/04/heres-why-you-may-be-buying-blackberry-again/
\end{thebibliography}

>>>>

\documentclass[12pt]{article}
\usepackage{latexsym}
\usepackage{setspace}
\usepackage{graphicx}
\graphicspath{ {/} }

\doublespacing

@@

There a wide range of Private Enhancing techniques using Crypotgraphy. This paper will focus on Private Digital Credentials, Type X remailers, Onion Routing, and Transport Layer Security while highlighting on how these can allow for digital privacy. A few defintions to establish are anonymity and pseudonymity. Anonymity systems are built to make one-way communication while getting information private while pseudonymity are built to allow for two-way communcation by using a pseudonym to help keep information private. \cite{GoldbergTwo}

@@

\section{Type X Remailers}\label{sec:type-x}
What is it?
The initial focus on prviacy dealt with email. One initial approach was have a third party remove all identifying information and then forward the message to the intended recipent. The other approach was to create a fake email with false information sometimes refer to as pseudonym. Hence people starting creating systems to reduce the work of the user trying to protect their information.

These anonymous remailer which aim to allow users to allow for e-mail communcations without losing privacy. There are four differ Versions of Type X Remailers, Type O, Type I, Type II and Type III with Type III providing the most functionality. All the different versions work differently where some are anonymity systems and others are pseudonym systems.

Type 0 remailer was also called anon.penet.fi \cite{GoldbertTwo}. It allowed for pseudonym commuication by having a table the matched the email addresses to the pseudonym. The recipent could respond and the Type 0 remailer would use the table to send the email back to real mail address. The service was shut down and only offers minimal security \cite{GoldbertTwo}.

Type I was also known as Cypherpunk was designed to address the security issues of Type 0. The major changes included no pseudonyms, encrypt/decrypt messages, and uses chaining. Chaining is the idea of sending the message through various remailers to make it more difficult to trace through. Type I was also combined with encryption to make it more difficult to intercept and read the intended message. Type II which was also known  Mixmaster added in more security to deal with certain types of eavesdroppings attacks such as correlation.

Type III is also known as Mixminion and had its first release in 2002. Mixminion aimed to support pseodonymity in which Type II had poor support\cite{GoldbertTwo}. The project had its own git on Github which has not been updated since 2011. According to their design document which can be found on their website, the designers had the following goals simplicity for clients, simple to deploy, and drop packets-level compatibility with Mixmaster (Type II).  Mixminon uses a free-route mix but does not implement reusable reply blocks.

Anonymous Remailers can be used to send communications anonymously. However Type III  has been said to not be trusted for anonymity \cite{GoldbertTwo}. The previous version have their technical issues. This details would need to be sorted out before this techonlogy can be confidently replied upon.

@@

\section{Transport Layer Security}\label{sec:tls}

Transport Layer Security (TSL) protocol is the successor of Secure Socket Layer protocol. It is supported in all modern browswers such as Chrome, Firefox, and Internet Explorer. TLS is a protocol which ensures information is transmitted securly. Transport Layer Security was designed to prevent eavesdropping and ensures information is not intercepted and changed during transmission \cite{Sidhpurwala}.

The protocol first exchanges keys using a key exchange. The data is then encrypted using a specified encyrption function such as AES. A message authencating code (MAC) is also created. The encyrpted text and th MAC is sent. The encyrption does not allow for eavesdropper to read the intended message. The MAC does not allow the user to intercept the message and change it.

The client will request to use Transport Layer Security and which initiates the Transport Layer Security handshake \cite{Sidhpurwala}.  The Transport Layer Security handshake has the six following steps:
\begin{enumerate}
	\item ClientHello: The client initial message that specifies supported Transport Layer Security versions, cipher suits, and compression methods. 
	\item ServerHello: The server responsed with a message that specifies with version of Transport Layer Security, cipher suit, and compression method to use. The message also contains an a random generated string $r$.
	\item ClientKeyExchange: The client generates a secret $s$ using the server public key. The client than transmits a record called ClientKeyExchange along with the secret $s$. Client and server use $r$ and $s$ to create a Master Secret. 
	\item ChangeCipherSpec: The client then sends a message which signals all information will be encrypted. The client then proceeds to send the encrypted message and authentication. 
	\item ChangeCipherSpec(response): The server response to the clients message.
\end{enumerate}

\includegraphics{tls-handshake}

 Transport Layer Security is a widely used. Transport Layer Security is a good example of when standards are created then people will follow them. It is not difficult to enable a web application to support Transport Layer Security through various libraries such as OpenSSL. There are still problems with TSL/SSL and this was shown recently through the HeartBleed Bug. HeartBleed was a good example of the lack of funding applied to security budgets.

\section{Companies doing Security Right}\label{sec:real-life}
Wickr is a new messenger which is available on Google Play store, Apple App Store, and even for desktop. It is uses peer-to-peer encryption and enables users to send encrypted messages.  According to its website it uses hashed all device information with SHA256 and encrypts all data with AES256. The Wickr server only handles encrypted messages and delete the message upon delivery. The server also never directly interacts with devices identifiers but onlt the hashes of them. Wickr has received four and a half stars on the Apple store from 80 different ratings and has a similar rating on the Google Play store.

@@

\bibitem{Marks}
	Marks, G. (2014, March 4). Here's Why You May Be Buying BlackBerry Again. Retrieved December 5, 2014, from http://www.forbes.com/sites/quickerbettertech/2014/03/04/heres-why-you-may-be-buying-blackberry-again/

\bibitem{Sidhpurwala}
	Sidhpurwala, H. (2013, July 24). Transport Layer Security. Retrieved December 6, 2014, from https://securityblog.redhat.com/2013/07/24/transport-layer-security/
\end{thebibliography}
